systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-16 paper/trunk/systemfit_other.tex
added description of methods "WSUR" and "W3SLS"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@599 591db2bd-e0a0-4d22-8c19-2192dbb7da31

The WLS, SUR, W2SLS and 3SLS parameter estimates are consistent,
if the estimated residual variance-covariance matrix is calculated
using the residuals from a first-step OLS or 2SLS estimation.
It is also possible to iterate the estimation procedure and 
calculate the residual variance-covariance matrix from the
residuals of the previous iteration. 
If equation (\ref{eq:rcov0}) is applied to calculate the estimated
residual variance-covariance matrix, the results converge to maximum
likelihood \citep[p.\ 345]{greene03}.

>>>>

The WLS, SUR, W2SLS and 3SLS parameter estimates are consistent,
if the estimated residual variance-covariance matrix is calculated
using the residuals from a first-step OLS or 2SLS estimation.
The software LIMDEP calculates SUR or 3SLS estimates by a
slightly different approach.
It uses the residuals of a first-step OLS or 2SLS estimation
for a second-step WLS or W2SLS estimation,
and then calculates the residual variance covariance matrix
from the residuals of the WLS or W2SLS estimation
to estimates the model by SUR or 3SLS in a third step
\citep{greene06}.
It is also possible to iterate the estimation procedure and
calculate the residual variance-covariance matrix from the
residuals of the previous iteration. 
If equation (\ref{eq:rcov0}) is applied to calculate the estimated
residual variance-covariance matrix, the results converge to maximum
likelihood \citep[p.\ 345]{greene03}.
